PyUltraLight: A Pseudo-Spectral Solver for Ultralight Dark Matter Dynamics

### 2018-10-03 draft.tex
removed comments from text

\re{I think this is mostly there, but we should say which surface integral and may cite some of the literature here}\ek{How's this? It seems to be difficult to find many references which explain the subtraction of the average in detail, a lot of people just seem to use it without explanation.}

@@

Figure \ref{fig:comparison} shows profiles of the density through the simulation volume, as a function of spatial resolution and timestep.  Each plot represents the density profile down the axis of symmetry of the initial configuration (vertical axis in Figure \ref{fig:disruption}) after approximately half a revolution around the central potential, or t=0.28 code units -- slightly after the final frame in Figure \ref{fig:disruption} - when the solitons have become distorted due to tidal forces, but are not yet completely disrupted. We see that as the timestep is varied from 0.1 to 50 times the default value, the results with the default and the shorter timestep are virtually indistinguishable, and results are still reasonably accurate at 10 times the default timestep, with small deviations at high densities. However, the results are significantly distorted at 50 times the default timestep. We also see that as the spatial resolution is decreased from $320^3$ to $64^3$, the lowest resolution performs poorly, but there is good convergence  at resolutions of $192^3$ and above. \re{minor edits; we could do the two figures as a single image}\ek{How's this?}

@@

\begin{figure} 
  \includegraphics[width=1.\textwidth,trim=0 1cm 0 2cm,clip]{combined}
  \caption{Top: Phase deviation of $\psi$, relative to solution with timestep 0.1 times default, sorted by the density. There is excellent agreement with the default timestep, and reasonable convergence at steps up to $10$ times the default, with better accuracy in high density regions. Bottom: Difference in magnitude of $\psi$, relative to the  solution with timestep 0.1 times default. Again we see good convergence with the default timestep, and tolerable agreement in high density regions when the step is a factor of $10$ or less than default. \re{Do we want to the put the ``key'' at the bottom not the middle; also I think the $x$-axis label could be clearer, or dropped.}}\ek{How's this?}
  \label{fig:temporal}
\end{figure}
\clearpage

>>>>

@@

Figure \ref{fig:comparison} shows profiles of the density through the simulation volume, as a function of spatial resolution and timestep.  Each plot represents the density profile down the axis of symmetry of the initial configuration (vertical axis in Figure \ref{fig:disruption}) after approximately half a revolution around the central potential, or t=0.28 code units -- slightly after the final frame in Figure \ref{fig:disruption} - when the solitons have become distorted due to tidal forces, but are not yet completely disrupted. We see that as the timestep is varied from 0.1 to 50 times the default value, the results with the default and the shorter timestep are virtually indistinguishable, and results are still reasonably accurate at 10 times the default timestep, with small deviations at high densities. However, the results are significantly distorted at 50 times the default timestep. We also see that as the spatial resolution is decreased from $320^3$ to $64^3$, the lowest resolution performs poorly, but there is good convergence  at resolutions of $192^3$ and above.

@@

\begin{figure} 
  \includegraphics[width=1.\textwidth,trim=0 1cm 0 2cm,clip]{combined}
  \caption{Top: Phase deviation of $\psi$, relative to solution with timestep 0.1 times default, sorted by the density. There is excellent agreement with the default timestep, and reasonable convergence at steps up to $10$ times the default, with better accuracy in high density regions. Bottom: Difference in magnitude of $\psi$, relative to the  solution with timestep 0.1 times default. Again we see good convergence with the default timestep, and tolerable agreement in high density regions when the step is a factor of $10$ or less than default. 
  \label{fig:temporal}
\end{figure}
\clearpage
